\section{Alexander van Oostrum}

Being part of the structural department my main contribution lies within these parts of the reports. For the work up to the Baseline review this thus includes the structural literature study and requirements, appended with the general review of past missions, functional breakdown and design options. 

Within the context of the Mid-Term report my main contribution lies in the structural mass estimations and the remaining chapters not concerning a tool development, and editing of the report.

In the part regarding the structural mass estimates I have performed the isotensoid analysis and the rigid structural mass estimate modelling and helped in performing the verification of the remaining inflatable models.  The contents of the structural mass estimates chapter have been written in close collaboration with Bj\"{o}rn, both bearing responsibility for at least part of almost any section.

The remaining chapters not concerning a tool development includes parts of the work structuring, mission operations, design interfaces (N2 chart), trade-off table and a lot of general editing of the report.

Moreover for the Mid-term report I have worked on structuring the design options considerations trying to follow the group consensus.

Since for the midterm report no general stress analysis tools have yet been implemented due to the high variety of different concepts relatively, compared to the other technical departments, a lot of time was spend on the writing of sections of the Mid-Term report.  A stress analysis tool should be implemented for the next design phase working towards the final report. This should increase the (pure) technical contribution of the structures department which was up to this point below my personal liking. For the next design phase the focus should preferably move towards an increased technical contribution/tool development whereas it should be made sure that the remaining work is subdivided fairly over the group members.

Within this group I feel that there is a strong preference towards tool development resulting consequently in the remaining report components to be lacking in content. This should be monitored more carefully as there is a danger that these works become completely looked over. Specifically working as planner the danger lies/laid in rescheduling those task to myself (and Bj\"{o}rn). Deadlines are not the problem, rather the distribution of the report elements becomes skewed. Personal deadlines therefore may require/ required more strict handling. 

In terms of group functioning I believe, beside the above made point, there are no points worth the mentioning in regards to this group. 
 
