\section{Joost}

The first period, before the baseline review, I performed the literature study on control systems and analysed the control system requirements. I also extracted data from the MARS-GRAM2010 software and implemented a interpolation script that provides atmosphere data to the orbit and control software.

In the period between the baseline-review and the mid-term-review, my contributions have been on the aerodynamics software and text. I've written the code that solves the modified Newtonian flow for the given geometry, also outputting relevant plots for all concepts and analysing data for concept trade-off as well as validation. I made another interpolation script that allows for inputting the data in the orbit and control group.

Besides the technical contribution, I was the chairman during the first 5 weeks, leading the meetings with the tutor and coaches, and shaping discussions during the begin- and end-of-day meetings to ensure consensus while actively contributing with different insights in discussions. In this role I also presented the introduction to the mid-term review and lead towards a conclusion of the review.

About my performance in the team, I'm reasonably content. I think the work that was put in the aerodynamics tool was put to good use. However, I think at some times my time was spent inefficiently by not keeping track of what needed to be done and not coordinating collaboration well enough. This resulted in the fact that I didn't have time to work on other parts of the report than the aerodynamics part, which is a shame. My role as a chairman, I think, was done quite well as far as leading discussions goes. Luckily everyone in the group spoke up every now and then, so there wasn't a lot of work there. The planning should probably have been kept more sharp, and I think I should have contributed to that. It is hard to force decisions like halting the work on a certain task.

The project organisation as far as our direct instructor and coaches go is done well and professionally, which I like. However, deadlines are not always clear, are given late or are put on blackboard without notifying the group of that. This should improve. Furthermore, the fact that multiple documents exist that detail the same deliverables is a shame since this introduces a lot of unclarity.