\section{Suthes}

In the first half of the DSE I have been assigned to the verification activities as organisational responsibility and the thermodynamics of the heat shield as technical responsibility.

For the Project Plan and Baseline Report I have written a lot on the summary, introduction and conclusions. Furthermore I have wrote the parts on sustainable development for these two reports. Since my technical assignment was on the thermodynamics, the literature study on thermodynamics is jointly written by Lucas and me. At this point I have not yet been involved in any of the verification activities.

For the Mid Term Review, Lucas and I have been busy with the development of thermal analysis tool. The actual coding behind the tool was finished quite quickly. However during the verification process a bug was found. During the project hours Lucas and I have tried to fix the bug, and in my free time I have tried to find the problem as well by for example rewriting the code again. Four days before the deadline we decided to postpone the tool development and focus on getting at least some result for the TPS-mass. In these days I focussed on finishing the part on TPS and other things the report. For now I cannot say that I am satisfied with the progress we made as the thermodynamics group, so that is something we have to work on for the second half of the project. From now on, I shall also write the meeting minutes.

About the group dynamics I think we have a very capable and well-functioning group. I really think everyone is able to contribute to discussions and decisions. Personally I think I have contributed less than average to these discussions, as I feel almost everything is already covered by others. For the second part of the project I do not think I should change that, since it will only unnecessarily lengthen discussions (as my opinion is very often expressed by others). Of course, my technical performance and contribution should be a lot better, such that we get actual results in the final review for thermal protection system.