\section*{Summary}\label{cha:summary}

To fulfill the need to carry human payload to Mars one solution is a \acrfull{cia}. The project has to demonstrate the feasibility of such a controllable inflatable aeroshell. The design of this product can be considered as complex. The first steps in simplifying the design process have been summarized in the \acrfull{pp}. The next steps include a literature study to familiarize with the subject. This literature study consists of an analysis on past solutions alongside with the investigation of the primary disciplines involved in the design of a re-entry mission. Then a functional and requirements analysis is performed to generate design options for the different mission aspects of the re-entry vehicle. This baseline report also comprises the market analysis, budget breakdown, risk assessment and an approach with respect to sustainable development. Also a tool is developed and presented to make early predictions for the astrodynamic characteristics. 

To arrive at the concepts shown in a \acrfull{dot}, it is advised to start with a functional analysis. In this analysis a \acrfull{ffd} is made to show the logical order of functions the re-entry vehicle must perform. The functions can also be categorized in a \acrfull{fbs}. Then the requirements are analyzed. This is done using a requirements discovery tree which shows how different subsystem requirements flow down from the top level requirements and constraints. The list of requirements is summarized in Appendix \ref{app:req}.

A market analysis is performed which aims to minimize the risk of selecting a wrong combination of function and technology for the customer. A \acrfull{swot} analysis provides an overview of the primary characteristics of the proposed \gls{cia}. The design process is exposed to several risks, primarily schedule overruns and insufficient technical performance. In order to identify, analyze and manage risks a risk mitigation plan is made, which uses risk mapping as a qualitative method and Technical Resource Budgeting (TRB) as a quantitative method. Within this mission, sustainability will not have the highest priority in the design process since the total impact of a single interplanetary mission on the environment is relatively small. It will, however, play a role when faced with design choices. If budgets and technical performance allows, a more sustainable design is the preferred one.

After this the initial design concepts are generated. For this a \gls{dot} is used. First a \gls{dot} for each of the following aspects is constructed: the trajectory, the shape and the control. In the separate trees the fully unfeasible options are eliminated. Then feasible combination of the options in the three trees are sought.

This baseline report is concluded with the feasible combinations of the concept-options. Future work includes narrowing down the design options to five concepts. In the \acrfull{mtr} these concepts will be reviewed and a trade-off process will help with the selection of the final concept that shall be designed with more detail for the \acrfull{fr}.
