\section{Organisational Function Description} \label{app:obs}
The functions, as described in section \ref{sec:org}, entail the following responsibilities.

\subsubsection{Chairman}\label{subsec:Chairman}
\input{./OBS/Chairman}

\subsubsection{Secretary}\label{subsec:Secretary}
\input{./OBS/Secretary}

\subsubsection{Documentation manager}\label{subsec:D_and_A}
\input{./OBS/D_and_A}

\subsubsection{Planner}\label{subsec:Planner}
\input{./OBS/Planner}

\subsubsection{Systems engineer}\label{subsec:SE}
\input{./OBS/SE}

\subsubsection{Risk Engineer}\label{subsec:RiskEng}
\input{./OBS/RiskEng}

\subsubsection{Quality assurance}\label{subsec:QA}
\input{./OBS/QA}

%\subsection{Engineering breakdown}\label{subsec:engineer}
%The engineering work of the controllable inflatable aeroshell is divided into different departments. These departments are the driving fields in the design of an inflatable aeroshell and will cover all aspects of the design. As for the management positions, engineering departments are not isolated in the sense that the aim is to involve team members in multiple design aspects.

\subsubsection{Aerodynamics department}\label{subsec:aero}
The aerodynamics department will look at different shapes possible to do the entry in the Martian atmosphere. This department looks at the hypersonic aerodynamics and determines the amount of thermal energy the heat shield needs to absorb and the loads that the structure needs to endure. In addition, the creation of a aerodynamic model of the vehicle that will be used in the control system is produced by the aerodynamics department.

\subsubsection{Structures department}\label{subsec:struct}
The structures department is responsible for the design of the structure, carrying primarily the mechanical and thermal loads by aerodynamic forces and heating. This design entails appropriate material selection, design and sizing of load-carrying elements and integrating the design while maintaining feasibility in terms of manufacturability, costs and weight. For the purpose of determining structural performance, the structures department is responsible for the development of structural tools. Moreover, the structures department actively communicates with other departments to synthesize the system design.

\subsubsection{Control systems department}\label{subsec:control}
The control systems department will analyze the controllability and stability, both static and dynamic, of the vehicle. Further this department will design the subsystems that will provide the needed characteristics for the controllability and stability. The control department covers all additional subsystems to ensure a controllable and stable vehicle, i.e. an attitude determination system. It will also create the astrodynamic mission profile to be used during the re-entry, and will create a model of the Martian atmosphere to use during the determination of this profile.

\subsubsection{Thermal control department}\label{subsec:therm}
The thermodynamics department will look at the thermal aspect of the inflatable aeroshell. The aerodynamics department will provide a boundary condition for the heat propagation within the structure. This heat propagation will be dependent on material properties and structure shape as defined by the structures department. Furthermore, the space vehicle should have thermal control such that systems can operate and humans can survive.