\section*{Summary}\label{cha:summary}
There is an increasing demand for carrying human payload to the surface of Mars, and inflatable aeroshell concepts hold the key to what is currently unattainable for interplanetary human spaceflight. In the wake of current \acrshort{nasa} investigations on the feasibility of inflatable decelerators for hypersonic guidable entry, this study focuses on the preliminary design of a controllable Mars entry vehicle with a payload mass of at least $9000 \left[kg\right]$ using an inflatable aerodynamic decelerator of at most $1000 \left[kg\right]$. Such a solution provides a large economical advantage over conventional solutions by maximizing payload-carrying capability through a lightweight device less burdened by launcher size considerations. Altogether, the objective is to design an \acrfull{cia} for a spacecraft capable of carrying human payload to Mars.\\

To aid in the design of such a vehicle several tools have been developed with the following purposes:

\begin{itemize}
\item A tool for parametric structural mass modelling
\item A modified Newtonian flow aerodynamic tool for the characterisation of aerodynamic and aero-thermal behaviour and shape optimisation
\item A thermal model for \acrlong{tps} sizing and analysis
\item A trajectory tool with an implemented control system for trajectory control
\end{itemize}
\vspace{1mm}
This results in a vehicle that has an undeployed diameter of $5 \left[ m \right] $ and a deployed diameter of $12 \left[ m \right]$. It is designed for an entry velocity of $7 \left[ km \cdot s^{-1} \right]$ and a final velocity of Mach $5 \left[-\right]$ at  $15 \left[ km \right] $ altitude within a horizontal precision range of $500 \left[ m \right]$. To this extent the $10\mbox{ }000 \left[ kg \right]$ vehicle has a aerodynamic decelerator mass of $928 \left[ kg \right] $ including contingency. Due to the human payload the mission is sized for an acceleration below $3\gls{con:ge}$. Furthermore, the maximum aerocapture and entry phase duration is 10 days, where two periods of aerodynamic deceleration exist. During both manoeuvres, aerocapture and entry, the vehicle will spend up to $800 \left[ s \right]$ in the Martian atmosphere. In between aerocapture and entry the vehicle will be placed in a parking orbit. The vehicle adheres to \acrfull{cospar} regulations and has a control system reliability of $0.9995 \left[ - \right] $.
\newline
\newline
A key feature of the \acrshort{cia} is its asymmetric, skewed shape. The asymmetry follows from aerodynamic optimisation and yields higher lift-generating capability at lower angles of attack to firstly achieve more lift and secondly require smaller angles of attack to keep the crew module from being exposed by the flow. Aerodynamic performance is characterised by a 0.35 lift-to-drag ratio and a $22.5\left[deg\right]$ trim angle of attack.
\newline
\newline
The asymmetry is adopted by the structural shape through stitching of ten inflatable toroids at a variable half-cone angle with respect to one another. Structural rigidity under an ultimate aerodynamic pressure of $3500 \left[Pa\right]$ is ensured by the use of a nitrogen blow-down system that inflates five bladder volumes at $169 \left[kPa\right]$, which keeps the flexible bladder material in tension to prevent compressive wrinkling. Resulting loads are carried by woven PBO Zylon\textsuperscript{\textregistered} fibres of $0.125 \left[mm\right]$ thickness at a $95 \left[kg\right]$ mass. At a minimum half-cone angle, the structural mass is estimated at $300 \left[kg\right]$. 
\newline
\newline
The \acrlong{tps} is exposed to a peak heat flux of $21 \left[W \cdot cm^{-2}\right]$ and a peak temperature of $1376 \left[K\right]$ during aerocapture. This thermal loading is withstood by a multi-material lay-up $256 \left[kg\right]$ consisting of a state-of-the-art Nicalon\textsuperscript{TM} barrier of $0.51 \left[mm\right]$ thickness and Pyrogel\textsuperscript{\textregistered} 6650 insulator of $2.4 \left[mm\right]$ thickness, complemented by dual $25 \left[\mu m\right]$ Kapton gas barriers. 
\newline
\newline
Compatibility of the \acrshort{cia} with a manned Mars mission is ensured by preliminary crew module and mission design. The crew module accommodates two crew members for a 100-day interplanetary mission and its mass is estimated at $9000 \left[kg\right]$. Return from Mars requires two launches prior to crew module launch, which bring the \acrlong{mav} onto Mars and an \acrlong{erv} in an orbit around Mars. Mission cost is estimated at 44 billion US dollars.
\newline
\newline
Recommendations are a propagation of design on decelerator and crew module, testing activities, and crew and mission preparation thereafter. Key driver for further design is concept reliability. Deployment, inflation and terminal descent are critical mission phases and inherently unreliable for a \acrshort{cia} design. These therefore require particular attention in future design.
