\section{Alexander van Oostrum}

For the work up to the final report I have primarily been working on the structural subsystems. This was again in close collaboration with Bj\"{o}rn. Moreover, in the last week(s) of the final design I have been working on the control system, primarily working on the control actuation, mass estimate, and the little bit on the possible implementations. I still believe that the control system is maybe a bit neglected. Off course, however, choices are always to be made and I am happy with the end result. Also again a lot of editing happened and also other sections were worked on as stated in the logbook.

Whereas I had a little doubt whether we were heading the right direction this completely disappeared after the mid-term review. The task within the group were much better divided and more people took responsibility. This consequently meant that I pulled back a little bit on leadership as it was no longer a necessity as more people pulled in on this. The focus was put more towards producing a actual design and we really worked together as a team. 

I think a significant risk was taken by laying a focus on the tool development but in the end this worked out well. This meant that a lot of the results for the final design are actually based on calculation supported by an analysis and were not made arbitrarily. This was much to my personal liking. Still, in the beginning maybe a bit longer had to be looked at available literature on what is achievable and conventional. To my personal liking to much time was spend on the not HIAD related design elements. This is however more a result of the DSE requirements and not so much based on group decisions.

I truly enjoyed working with this group and I am happy with the end result. The tasks within the group were properly distributed and everybody has been useful and responsible for some parts of the report.
