\section{Bj{\"o}rn van Dongen}
This chapter details the personal contributions of Bj{\"o}rn van Dongen as performed in the Design Synthesis Exercise (DSE).

As structural analyst, my function up to the Baseline Review (BR) was to investigate the means to retain structural stiffness primarily for inflatable concepts. Hereafter structural analysis of the five concepts prior to the Mid-Term Review (MTR) was difficult by their structural diversity. Since structural performance is reflected by mass, based on the premise that mass can be added until sufficient structural integrity is achieved, I implemented mass estimation tools for stacked toroid, tension cone and trailing ballute concepts and analysed their outputs. 

After the MTR, structural analysis proceeded in detail by cooperation with Alexander to implement a load estimation tool. This tool, in the form of a quasi-3D truss model, allowed sizing and feasibility assessment of the stacked toroid structure. In addition, deployment and inflation system were key components in the design under my and Alexander's responsibility.

Moreover, my technical function has extended to work-supporting activities, such as the work definition, design interfaces and market analysis. I have been in charge of retaining the overview, structuring and documentation of the trade-off process and as systems engineer in the packaging and design of the crew module.

As editor up to the MTR, a significant part of my time has been put into the written deliverables. I have set up a set of guidelines to which team members shall adhere, actively controlled that the guidelines are adhered to, proof-read all parts for contents-wise and textual correctness, implemented corrections and set up report and chapter structure. My performance in this function is reflected by the reports delivered, both in the chapters of other group members as well as in those chapters not corresponding to a technical department, such as the trade-off.

I feel satisfied with my performance as editor, but it has required me to commit a significant amount of time otherwise spent on structural analysis. Other team members have been so taken up in their tools at times, that other contributions are often lacking and intervention, by myself and Alexander mostly, is necessary to ensure that all content is covered. As systems engineer, my job was significantly eased by great team chemistry and a carefully thought-out design and iteration process that ultimately led to the final design. 
%\begin{table}[h]
%\caption{Written contributions of B.R. van Dongen}
%\centering
%\begin{tabular}{|p{0.1\textwidth}|p{0.565\textwidth}|}
%\hline
 %\textbf{Report}   & \textbf{Written}                                                                                             \\ \hline
%BR  & Section 2.3, Ch 4, Section 5.4, Ch 7, Ch 10                                                           \\ \hline
%MTR & Introduction, Summary, Ch 2, Ch 3, Ch 5, Ch 6 (partially), Ch 7 (partially), Ch 10, Ch 13, Conclusion \\ \hline
%\end{tabular}
%\end{table}

I highly enjoy and appreciate the dedication and company of all group members. Work output is high for all group members and I find the work experience enjoyable. Team performance is highly satisfactory and we have been a tight-knit group of team members throughout the entire DSE.


