\section{Dawud Hage}

	%Each person briefly explains on one page A4 his/her activities and gives a personal impression about his functioning, the project, the team, the cooperation, the organisation, the staff, etc.

In the passed ten weeks I worked on the trajectory- and control tool together with Twan Keijzer. This was a big challenge because of the complexity of it, if not the right assumptions are made the problem can easily become to large for the scope of the DSE. It is nice to see how this tool integrates all the different parameters.

The organizational function I had to fulfil in the first half of the DSE was the job of documentation manager. For the first two weeks this was quite a lot of work, setting up the right structure for LaTeX, Dropbox folders and Mendeley. However after the initial set-up the rest of the group quickly adapted to use the documentation system therefore my work was done, except for small changes every now and then.

For the second half of the DSE (from the mid-term onwards) my organizational function was the chairman. This included to guide the group to the final design, make decisions where the discussions were endless. I tried hard to make sure that everyone was involved and felt comfortable with the choices. It was fun to do and I learned a lot.  

About the team, I think that our DSE group is a productive and fun group. It was really nice to work in this DSE group, I never expected to be put into a group that would be so easy to work with. There was room for serious work and of course for fun discussions. Today we had the discussion if bananas are trees or plants, it escalated quickly to the discussion of what are berries? These discussions are creating an even better team spirit. It is also nice that there is a big diversity in interests. I cannot imagine a better group to do the DSE with.