\section{Joost Meulenbeld}


The first period, before the baseline review, I performed the literature study on control systems and analysed the control system requirements. I also extracted data from the MARS-GRAM2010 software and implemented a interpolation script that provides atmosphere data to the orbit and control software.

In the period between the baseline-review and the mid-term-review, my contributions have been on the aerodynamics software and text. I've written the code that solves the modified Newtonian flow for the given geometry, also outputting relevant plots for all concepts and analysing data for concept trade-off as well as validation. I made another interpolation script that allows for inputting the aerodynamic data of a design in the orbit and control group. After the mid-term-review, I implemented an optimisation method to optimise the aerodynamic shape towards certain objectives. Together with Guido, I found out the proper optimisation criteria.

Alongside the aerodynamic optimisation, I conceptualised the terminal descent phase and calculated an estimate on its fuel and thruster mass. I created the Gantt chart detailing the development phase after the DSE.

Besides the technical contribution, I was the chairman during the first 5 weeks, leading the meetings with the tutor and coaches, and shaping discussions during the begin- and end-of-day meetings to ensure consensus while actively contributing with different insights in discussions. In this role I also presented the introduction to the mid-term review and lead towards a conclusion of the review. The second quarter, I was the planner of the DSE group. I made the planning and made sure everyone was up-to-date on it, using a calendar that was printed out and put on the wall. While I was not the chairman anymore, I still made an effort to stay informed about what other people were doing.

About my performance in the team, I'm reasonably content. I think the work that was put in the aerodynamics tool was put to good use. My role as a chairman, I think, was done quite well as far as leading discussions goes. Luckily everyone in the group spoke up every now and then, so there wasn't a lot of work there. The planning should probably have been kept more sharply, and I think I should have contributed to that. It is hard to force decisions like halting the work on a certain task. After the mid-term, planning didn't take as much time, but I think the calendar on the wall was a good thing. I kept an overview of the work that needed to be done.

The project organisation as far as our direct instructor and coaches go is done well and professionally, which I like. However, deadlines are not always clear, are given late or are put on blackboard without notifying the group of that (which is a responsibility of the OSSA's, I think). This should improve. Furthermore, the fact that multiple documents exist that detail the same deliverables is a shame since this introduces a lot of unclarity.