\section{Suthes Balasooriyan}
Now that we are finishing up with the DSE, this second personal appendix is served to sum up my experiences of this DSE. For my extensive recount on the first half of the DSE I would like to refer you to the first personal appendix. However, I will start with a small summary.

In the first half of the DSE I had been assigned to the verification activities as organisational responsibility and the thermodynamics of the heat shield as technical responsibility. For the Mid Term Review, Lucas and I have been busy with the development of thermal analysis tool. The actual coding behind the tool was finished quite quickly. However during the verification process a bug was found. At this point I could not say that I was satisfied with the progress we made as the thermodynamics group, so that is something we had to work on for the second half of the project.

For the second half of the project I would continue with my work on thermodynamics. Furthermore, to increase my organisational responsibilities within the group I have been writing the minutes for the meetings. Writing the minutes during the meetings was not an extra burden, processing them took more time than expected. For the technical aspect we made very good progress and the end result is something I am very satisfied with. 

About the group dynamics I think we had a very capable and well-functioning group. I really think everyone has been able to contribute to discussions and decisions. Personally I feel I have contributed less than average to these discussions. However, for the second part of the project I have tried to change that, since it was something others remarked during the mid term peer review. My technical performance and contribution has been a lot better, as we got actual results in the final review for thermal protection system. All in all I am satisfied with the overall performance of the group. Furthermore, the group was very nice to work with.