Cost can be split up into two sections: Development cost and production cost. Whereas the development-related costs consist of non-recurring expenses, the production cost is dependent on the number of missions to be carried out. The analysis by Wertz et al. \cite{Wertz2011} will be used to determine the costs associated with these components. Since these are determined in constant 2010 US dollars a factor accounting for inflation is used. This factor was found by looking at the \gls{cpi} ratio between April of 2010 and 2015. From Reference \cite{Crawford2015} this factor was found to be $1.075$, corresponding to an inflation over five years of $7.5\%$.\\
For the development and production cost a \gls{cia} propellant mass of $153$ $\left[kg\right]$ was used, conform to the final design presented in Chapter \ref{cha:finaldesign}. A total \gls{cia} mass (including propellant) of $1000 \left[kg\right]$ was assumed, in order to take into account the maximum allowable \gls{cia} mass growth. For the crew capsule a total mass of $9000 \left[kg\right]$ was assumed from which $700 \left[kg\right]$ of propellant mass was subtracted. The origin of this propellant mass will be covered in further detail in Chapter \ref{ch:crewmod}. In addition to the propellant mass the crew mass was also subtracted in order to arrive at the spacecraft dry mass.\\
Next to the \gls{cia} and accompanying crew module a \gls{mav} and an \gls{erv} are also needed to complete the mission. These vehicles fall outside of the scope of this report, but in order to estimate their impact on mission cost they will be taken into account in this section. A dry mass of $5000$ and $10\mbox{ }000 \left[kg\right]$ was assumed for these vehicles respectively.

\subsubsection{Development costs}
In contrast to the total mission the development costs consist of those incurred by \gls{cia} and capsule development. Atgar \cite[p.296]{Wertz2011} presents the development cost per kilogram of dry mass for various vehicles. These values, together with the total development cost are shown in Table \ref{tab:devcosts}.

\begin{table}
	\centering
	\caption{Development costs in 2015 US dollars}
	\begin{tabular}{|c|p{5cm}|p{5cm}|}
		\hline
		\textbf{Cost component} & \textbf{Development cost per kg dry mass $\mathbf{[2015}$ $\mathbf{US\$]}$} & \textbf{Total development cost $\mathbf{[2015}$ $\mathbf{million \mbox{ } US\$]}$} \\ \hline \hline
		\gls{cia} & 2 569 000 & 2 176 \\
		Crew module & 1 255 000 & 10 216 \\
		\acrlong{mav} & 2 569 000 & 12 845  \\
		\acrlong{erv} & 1 255 000 & 12 550  \\ \hline
		\textbf{Total} & - & 37 786 854 \\
		\hline
	\end{tabular}
	\label{tab:devcosts}
\vspace{-2mm}
\end{table}

\subsubsection{Production costs}
The production costs were determined in similar fashion to the development costs presented in the previous section. Table \ref{tab:productioncosts} shows the corresponding productions costs per kilogram of dry spacecraft mass and for the complete respective component.

\begin{table}[h]
	\centering
	\caption{Production costs in 2015 US dollars}
	\begin{tabular}{|c|p{5cm}|p{5cm}|}
		\hline
		\textbf{Cost component} & \textbf{Production cost per kg dry mass $\mathbf{[2015}$ $\mathbf{US\$]}$} & \textbf{Total production cost $\mathbf{[2015}$ $\mathbf{million \mbox{ } US\$]}$} \\
		\hline \hline
		\gls{cia} & 341 000 & 289 \\
		Crew module & 173 000 & 1 408 \\ 
		\acrlong{mav} & 341 000 & 1 705 \\
		\acrlong{erv} & 173 000 & 1 730 \\ \hline
		\textbf{Total} & - & 5 132 \\
		\hline
	\end{tabular}
	\label{tab:productioncosts}
\vspace{-2mm}
\end{table}

\subsubsection{Mission costs}
In addition to the costs incurred by the spacecraft themselves the overall mission architecture requires the use of additional resources such as launch vehicles. Assuming that two \gls{sls}' are needed to position all required vehicles mentioned in Section \ref{sec:missionoutline} around Mars (including the mission carrying the \gls{cia} and associated crew module) the mission item cost can be determined by summing these launch costs with the aforementioned production costs. For the launch of the \gls{sls} no official cost figure exists, though \gls{nasa} officials have been quoted as mentioning a goal of $500$ million US dollars per launch\footnote{URL: \url{http://www.nbcnews.com/id/49019843/ns/technology_and_science-space} Accessed: 18-06-2015}. As such the total launch cost per mission adds up to 1 billion US dollars.

%A more realistic 1 billion US dollars estimate is favoured to this optimistic estimate.

\begin{table}[H]
	\centering
	\caption{Overview of total costs for one mission}
	\begin{tabular}{|c|c|}
		\hline
		\textbf{Cost component} & \textbf{Cost $\mathbf{[2015}$ $\mathbf{million \mbox{ } US\$]}$} \\ \hline 
		\hline
		Vehicle development & 37 787 \\
		Vehicle production & 5 132\\
		Launch & 1 000\\ \hline
		\textbf{Total} & 43 919\\ \hline
	\end{tabular}
	\label{tab:missioncosts}
\end{table}

By combining the cost figures presented here the results presented in Table \ref{tab:missioncosts} were obtained. If more than one mission using these spacecraft is to be conducted the average cost per mission will be considerably lower than the total cost presented in Table \ref{tab:missioncosts} since the development costs are non-recurring expenses. This would also increase the cost-effectiveness of manned spaceflight to Mars.