In this section the mission requirements for the aerocapture and entry phase as described in Section \ref{sec:missionscope} are outlined and their origin is explained. A full list of requirements as defined top level can be found in Table \ref{tab:misreq} and \ref{tab:vehreq}.

The aerocapture and final \gls{edl} starts at the boundary of the atmosphere of Mars. Here the velocity of the entry vehicle is $7 \left[km \cdot s^{-1} \right]$. This requirement is imposed by the transfer trajectory that is taken from Earth to Mars. This trajectory should take as short as possible in order to both shorten the entire mission duration and decrease the physical taxation on the crew. The interplanetary transfer time corresponding to an entry velocity of $7 \left[km \cdot s^{-1} \right]$ is $89$ days. 

The mission ends at a speed of $M=5 \left[-\right]$ at $15 \left[km\right]$ altitude. At this point a terminal descent system takes over. The predetermined point at which the mission ends shall be reached with a precision of $500 \left[m\right]$. This requirement is imposed by the distance the final landing position can be from the provision. When the landing position lies too far from the provision a lot of time will be lost relocating the crew or crew members might not even be able to reach the provision.

While decelerating in the atmosphere the maximum deceleration shall not exceed $3\gls{con:ge}$. This requirement is imposed because of the limited capability of the crew to carry high deceleration loads.

The entry vehicle shall attain its final velocity within ten Earth days. This requirement is, just like the interplanetary transfer time, imposed both to shorten the aerocapture and entry phase duration and decrease the physical taxation on the crew. An additional reason for this time constraint is to limit the cost for and strain on the ground control crews that will be active continuously during the aerocapture and entry phase.


\begin{table}[h]
	\caption[Overview of mission requirements for the aerocapture and \acrlong{edl}]{Overview of mission requirements for the aerocapture and \gls{edl}}
	\label{tab:misreq} 
	\begin{tabular}{|p{0.12\textwidth}|p{0.85\textwidth}|}
    \hline
    \textbf{ID}          & \textbf{Description}                                                                                                      \\ \hline \hline
    CIA-M01& The entry vehicle shall decelerate from a velocity of $7 \left[km\cdot s ^{-1}\right]$ at $400 \left[km\right]$  \\ \hline
    CIA-M02 & The entry vehicle shall not exert an acceleration greater than $29.4 \left[ m \cdot s^{-2}\right]$ on any crew member for the duration of the mission			\\ \hline
    	CIA-M03 & The entry vehicle shall attain Mach $5 \left[-\right]$ at an altitude of $15\mbox{ }000 \left[m\right]$  \gls{mola} \\ \hline
    	CIA-M04 & The entry vehicle shall reach its final position with a precision of $500 \left[m\right]$\\ \hline
    	CIA-M05 & The entry vehicle shall attain its final velocity within 10 days after entering the Martian atmosphere \\ \hline
    \end{tabular}
\end{table}

\begin{table}[h]
	\caption{Overview of entry vehicle requirements} 
	\label{tab:vehreq}
	\begin{tabular}{|p{0.12\textwidth}|p{0.85\textwidth}|}
		\hline
		\textbf{ID}          & \textbf{Description}                                                                                                     \\ \hline \hline
		CIA-R01 & The entry vehicle shall have an undeployed diameter smaller than $5 \left[m\right]$                         				            \\ \hline
		CIA-R02 & The entry vehicle shall have a deployed diameter smaller than $12 \left[m\right]$                         				            \\ \hline	
		CIA-R03 & The entry vehicle shall have a mass of $10\mbox{ }000 \left[kg\right]$ at the start of the entry                       				            \\ \hline
		CIA-R04 & The hypersonic decelerator shall have a mass fraction of no greater than $10\%$ of the vehicle mass  \\ \hline
		CIA-R05 &  The entry vehicle shall adhere to the \gls{cospar} regulations \\ \hline
		CIA-R06 &  The entry vehicle shall have control system reliability of at least $0.9995$  \\ \hline
	\end{tabular}
\end{table}