\subsection{Overview of present and past (re-)entry vehicles}\label{cha:past missions}
<<<<<<< HEAD
This section gives an overview of (re-)entry vehicles, primarily to obtain a set of reference vehicles to aid design and sizing of the payload capsule in later stages and additionally to review solutions used in the past to perform (re-)entry for human spaceflight. At this point no structure supporting the deceleration has been chosen yet, as such only payload capsule size parameters are considered. It can be argued, based on human constraints, that the attached payload capsule for this mission will have similar characteristics. Table \ref{tab:refmis} displays some characteristics related to the payload capsule which can be used as indicative values\footnote{Principal values from: \\
URL: http://www.nasa.gov/sites/default/files/167718main\_early\_years.pdf,  Accessed: 28 April 2015 \\ URL: http://www.braeunig.us/space/  Accessed: 28 April 2015 \\ URL: http://wsn.spaceflight.esa.int/docs/Factsheets/35\%20Soyuz\%20LR.pdf Accessed: 28 April 2015
}
. For the descent module a separate retropack may be installed as was the case with the Gemini and Mercury missions.
=======
This section gives an overview of (re-)entry vehicles, primarily to obtain a set of reference vehicles to aid design and sizing of the payload capsule in later stages and additionally to review solutions used in the past to perform (re-)entry for human spaceflight. At this point no structure supporting the deceleration has been chosen yet, as such only payload capsule size parameters are considered. It can be argued, based on human payload constraints, that the attached payload capsule for this mission will have similar characteristics. Table \ref{tab:refmis} displays some characteristics related to the payload capsule which can be used as indicative values. 

>>>>>>> 0c3722e462c2edef474bc86fadfa037792f5ae48

\begin{table}[H]
	\caption[Reference missions for payload module sizing]{Reference missions for payload module sizing.}
		\begin{tabular}{|p{0.18\textwidth}|p{0.11\textwidth}|p{0.11\textwidth}|p{0.11\textwidth}|p{0.11\textwidth}|p{0.11\textwidth}|p{0.11\textwidth}|} % MAKE SURE THAT THE TOTAL WIDTH IS 0.95\textwidth!! (that way its exactly the textwidth.... haha) 
			\hline
			Mission 						& Apollo & 	Soyuz TMA &	Shenzhou & Gemini & Mercury & Orion \\ \hline \hline
			Years [$yr$]					&	1964-1975	& 	2010-2014&	1999- &   1959-1963  & 1959-1963 & Future \\ \hline
			Reentry module mass [$kg$]  	&	5806& 	2900 &	3240 & 3402 & 1118 & 8777 \\ \hline
			Habitable volume [$m^3$]		&	6.17& 	3.5  &	6.0  & 2.55 & 1.9 & 11   \\ \hline
			Diameter [$m$]			 		&	3.9 & 	2.17  &	2.52 & 2.3 & 1.9 & 5   \\ \hline
			Length  [$m$]			 		&	3.5 & 	2.24  &	2.5  & 3.4 &  5.2 & Unknown  \\ \hline
			Crew size (max) [$persons$]		&	3   & 	3     &	3    & 2   &  1   & 6   \\ \hline
		\end{tabular}
    \label{tab:refmis}
\end{table}


<<<<<<< HEAD
It must be noted that table \ref{tab:refmis} displays typical values only to be used as first indicative values. For example the diameter is typically a maximum value since no single value can be supplied due to the cone like shape of most reentry vehicles. Moreover these design include the size and mass of the deceleration mission of which the latter typically includes a heavy duty heat shield. Most reentry vehicle base designs were used multiple time with minor design changes and a single externally communicated design name. As such the values in the table above should be used with proper care as indicative values only. Habitable volume estimation also depends on the mission duration and may be considerable. A study on the estimation of these parameters is given by \cite{Rudisill2008}. Al tough this study focuses on a lunar mission/base it still underlines many of the important aspects with respect to payload module sizing which are applicable for mars mission as well. It may a such prove as proper foundation for payload module sizing. 
=======
It must be noted that table \ref{tab:refmis} displays typical values only to be used as first indicative values. For example the diameter is typically a maximum value since no single value can be supplied due to the cone like shape of most reentry vehicles. Moreover these designs include the size and mass of the deceleration mission of which the latter typically includes a heavy duty heat shield. Most re-entry vehicle base designs were used multiple times with minor design changes and a single externally communicated design name. As such the values in the table above should be used with proper care as indicative values only. Habitable volume estimation also depends on the mission duration and may be considerable. A study on the estimation of these parameters is given by \cite{Rudisill}. Although this study focuses on a lunar mission it still underlines many of the important aspects with respect to payload module sizing which are applicable for Mars missions as well. It may as such prove a proper foundation for payload module sizing. 
>>>>>>> 0c3722e462c2edef474bc86fadfa037792f5ae48

From the above mentioned reference missions in table \ref{tab:refmis} especially the future Orion mission, currently being designed, is of great interest.  [GIVE AN EXPLANATION]
