\section*{Summary}\label{cha:summary}%Notes: Stand alone, consise and do not explain anything.
-Requirements
-Description of the entire system (the Global Picture)

Ever since successful manned missions to the moon, then next step is a manned mission to mars. Re-entry in the atmosphere of mars induces great aerodynamic loads which lead to high thermal and structural loads on the structure. Where a spacecraft structure can be designed for very high loads, the human body is very limited in the loads it can endure. This creates the need for a system that can perform a re-entry on mars while keeping loads within the limits of what the human body can endure. A very promising design to perform such a re-entry is an inflatable guidable re-entry vehicle. Three designs have been made and tested by NASA and the next will be launched in 2016. \cite{irve2}(add 2 more ref. NASA) 

\subsection{Requirements}
In this section the top-level requirements are stated. They can be found in table \ref{tab:requirements}.

\begin{table}[H]
	\caption{Requirement}
	\begin{tabular}{|p{0.18\textwidth}|p{0.77\textwidth}|}
    \hline
    Requirement ID          & Description                                                                                                      \\ \hline \hline
    CIA-Sys-A01-1 & The re-entry vehicle shall be able to cope with an entry velocity of seven kilometers per second.                \\ \hline
    CIA-Sys-A01-2 & The inflated aeroshell shall have a maximum diameter of 12 meters.                                               \\ \hline
    CIA-Sys-A01-3 & The diameter of the launcher fairing shall be 5 meters.                                                          \\ \hline
    CIA-Sys-A01-4 & The maximum entry mass of the re-entry vehicle shall be 10,000 kilograms.                                         \\ \hline
    CIA-Sys-A01-5 & The hypersonic deceleration system mass shall not be heavier than ten percent of the total re-entry vehicle mass. \\ \hline
    CIA-Sys-A01-6 & The control system shall have a maximum failure probability of 5.0e-4.                                           \\ \hline
    CIA-Sys-A01-7 & The maximum allowable loads on the re-entry vehicle shall be 3 Earth g's in each axis                            \\ \hline
    CIA-Sys-A01-8 & The re-entry vehicle shall have a maximal aerobraking duration of ten days.                                      \\ \hline
    \end{tabular}
    \label{tab:requirements}
\end{table}

\subsection{System description}
Previous missions comparable to the present mission have been performed by NASA, demonstrating the controllability of an inflatable aeroshell, as early as the 1960's. Multiple concepts were developed: a chute that is held under tension with a pressurized toroid that was attached to the structure in one case and trailed the spacecraft using a tow in the other case. These concepts were developed to allow re-entry on Earth and Mars, but were discontinued when problems arised during deployment, and finally contemporary parachute technology proved sufficient for the design goals back then.
A pressurized cone containing multiple toroids is another option, one that receives considerable attention from NASA, in the form of three missions performed in the last ten years. A fourth mission is planned in 2016. Every next mission shows another aspect with respect to feasibility, controllability and ability to control the maximum deceleration achieved during re-entry.
These tests are now in the spotlight since interplanetary missions involving humans are on the program, with the NASA planning to have humans on Mars by 2030. Since transporting humans puts constraints on maximum deceleration, the present project may provide means to decelerate the interplanetary spacecraft with lower accelerations while still being a light-weight solution.




