\section{Concept structural mass estimation} \label{ch:strucmass}
It is essential that decelerator concepts are analyzed in terms of mass to fully appreciate the mass benefits of a certain decelerator concept. A reduced decelerator mass allows for a larger payload mass to be taken on board, since launcher mass capability is intended to be fully fulfilled. It is therefore essential that the concept selection takes into account decelerator mass. 

Concepts differ in the decelerator configuration and resulting mass differences between concepts are mostly due to structural and thermal mass. For a payload capsule and centerbody containing subsystems (e.g. telemetry, on-board computer) indifferent from the proposed five concepts, the decelerator structure, the \acrfull{tps} and the control system contribute to concept mass differences. To this end a structural mass estimation tool is constructed to provide an estimate of concept structural mass for an informed decision in the concept trade-off. 

Detailed structural analysis and design is held off until after concept selection, based on the premise that the structure can be sized such that all concepts are structurally feasible and any resulting differences in structural performance are reflected by total structural mass. Hereafter all references to mass are with respect to structural mass.

This chapter is structured in the following manner. Firstly, the purpose of tool development is outlined in section \ref{sec:strucpurp} to prevent a clear view of the required tool output. Based hereupon, a tool is constructed using a number of methods as described in section \ref{sec:strucmeth}. Verification and validation activities are described in section \ref{sec:strucvv}. The tools are then applied firstly to compare the selected decelerator concepts in terms of mass, as described in section \ref{sec:struccc}, secondly to provide an overview of the effect of materials choice on decelerator mass, as described in section \ref{sec:strucmat}, and lastly to perform a sensitivity analysis, as described in section \ref{sec:strucsens}.

\subsection{Purpose of tool development}\label{sec:strucpurp}
The purpose of the tool is twofold:
\begin{itemize}
\item To obtain a decelerator mass estimate for each of the five concepts in order to evaluate their mass performance;
\item To investigate the effect of concept design variables on decelerator mass;
\end{itemize}
The former is investigated primarily in section \ref{sec:struccc}, where the decelerator concepts are evaluated for their mass performance, while the latter is investigated in sections \ref{sec:strucmat} and \ref{sec:strucsens}. The mass estimate is primarily intended for relative comparison in this design phase, closed by the \acrfull{mtr}. It remains, however, a valuable tool in analysis and design of the selected concept by providing an actual mass estimate for a selection of design variables. This selection of design variables can thus be made using the mass estimate provided by the tool, by a minimization of decelerator mass.

\subsection{Methods for mass estimation}\label{sec:strucmeth}
\input{./Chapter/Structures/methods}
\subsection{Tool verification and validation}\label{sec:strucvv}
\input{./Chapter/Structures/vandv}
\subsection{Rigid concept mass analysis}\label{sec:rigid}   %Moet denk ik nog anders
\input{./Chapter/Structures/rigid}
\subsection{Inflatable concept comparison}\label{sec:struccc}
\input{./Chapter/Structures/comparison}
\subsection{Inflatable structural materials comparison}\label{sec:strucmat}
\input{./Chapter/Structures/materials}
\subsection{Sensitivity analysis}\label{sec:strucsens}
\input{./Chapter/Structures/sensitivity}
%\subsection{Conclusion}\label{sec:strucconc}

